LAGOS lake depth

### 2019-10-07 lagos_depth.Rmd
towards raster hypso panel

hypso_ct <- read.csv("data/ct_hypso.csv", stringsAsFactors = FALSE)
hypso_mn <- read.csv("data/mn_hypso.csv", stringsAsFactors = FALSE)
```

@@

>>>>

hypso_ct <- read.csv("data/ct_hypso.csv", stringsAsFactors = FALSE) %>%
  select(-n) %>% group_by(id) %>%  add_tally() %>% ungroup() %>%
  dplyr::filter(n > 3) %>%
  filter(!str_detect(id, "Cove"))
hypso_mn <- read.csv("data/mn_hypso.csv", stringsAsFactors = FALSE)
```

@@

```{r raster-to-profile-to-hypso}
# 3 panel figure of a single starting with rayshader, then depth profile, then hypsography

# use plotly::ggplotly to select specific lakes
dplyr::filter(hypso_ct, id == "lake_saltonstall") # super deep
"pickerel_lake" # convex
"long_pond" # concave

rsub1 <- raster::raster("data/ct_bathy/pickerel_lake.tif")
rsub2 <- raster::raster("data/ct_bathy/long_pond.tif")

# load hypso function(s)
get_hypso <- function(rsub, id){
  # rsub <- rsubs[[46]]

  maxdepth <- abs(cellStats(rsub, "max"))

  # calculate area of each class
  rc <- rsub %>%
    as.data.frame() %>%
    group_by(layer) %>% tally() %>%
    tidyr::drop_na(layer) %>%
    arrange(desc(layer)) %>%
    mutate(n_cs = cumsum(n)) %>%
    rename(depth = layer) %>%
    mutate(area_m2 = n_cs * res(rsub)[1] * res(rsub)[2]) %>%
    mutate(area_percent = scales::rescale(area_m2, to = c(0, 100))) %>%
    mutate(depth_percent = scales::rescale(depth, to = c(0, 100)))

  rc
}

names(rsub1) <- "layer"
hypso1 <- get_hypso(rsub1)
hypso1$test <- scales::rescale(c(diff(hypso1$n_cs), 0), to = c(0, 100))

ggplot(data = as.data.frame(rsub1, xy = TRUE)) + 
  geom_raster(aes(x = x, y = y, fill = layer)) +
  coord_quickmap()

cowplot::plot_grid(
ggplot(data = hypso1, aes(x = test, y = depth_percent)) +
  geom_point(aes(y = rev(depth_percent))) + xlab("Area (percent)") + ylab("Depth (percent)"), 
ggplot(data = hypso1, aes(x = area_percent, y = depth_percent)) +
  geom_point() + xlab("Area > depth (percent)") + ylab("Depth (percent)")
)

names(rsub2) <- "layer"
hypso2 <- get_hypso(rsub2)
